%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior DevOps Engineer - Developer Productivity} % Job title
    {Motive} % Organization
    {Remote, Pakistan} % Location
    {Mar. 2025 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected and optimized CI/CD pipelines using GitHub Actions and Tekton, achieving 40-50\% reduction in build and deployment times through workflow splitting and caching optimization for major repositories including KeepTruckin webapp.}
        \item {Resolved critical EKS infrastructure migration issues by troubleshooting and fixing node selector configurations, resource limits, and Auto Scaling Group (ASG) versions, ensuring seamless CI/CD execution across diverse environments.}
        \item {Led standardization initiatives for infrastructure tagging and owner conventions across AWS, Datadog, and GitHub, implementing automation via GitHub Actions to improve consistency and enable future infrastructure automation.}
        \item {Provided rapid incident response for release blockers and CI/CD deployment failures, collaborating with cross-functional teams (QA, SRE, application developers) to perform root-cause analysis and ensure production deadlines were met.}
        \item {Automated Tekton pipeline configurations for branch-specific node group assignments and resource management, eliminating manual interventions and improving deployment reliability for fleetcard and related services.}
        \item {Supported hotfix and emergency release cycles by manually managing cherry-picks, merges, and tagging when automation was insufficient, ensuring critical fixes reached production within tight SLA requirements.}
        \item {Enhanced technical documentation and onboarding processes in Confluence and GitHub, reducing new engineer ramp-up time and improving team knowledge sharing across the Developer Productivity organization.}
        \item {Championed automation of repetitive infrastructure tasks including pipeline configuration management, secret management policies, and owner tag standardization, maximizing team efficiency and reducing operational overhead.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior DevOps Engineer} % Job title
    {AERQ} % Organization
    {Hamburg, Germany} % Location
    {Apr. 2023 - Feb. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spearheaded the transformation of the DevOps team into a Platform team by developing an Internal Developer Platform, significantly enhancing team efficiency and collaboration.}
        \item {Architected and implemented an Infrastructure-as-Code (IaC) approach using Terraform and Terragrunt, streamlining infrastructure management and deployment processes.}
        \item {Deployed and managed a Kubernetes cluster in Azure (AKS), ensuring robust and scalable infrastructure for seamless application deployment.}
        \item {Successfully deployed and managed ArgoCD, Hashicorp Vault, Prometheus Stack, external DNS, and Cert Manager within the Kubernetes cluster, optimizing application management and security.}
        \item {Developed and maintained Helm charts and values files for multiple applications, ensuring consistent and efficient application deployment.}
        \item {Created GitLab pipelines for building and pushing Docker images and Helm charts, enabling efficient and reliable software delivery.}
        \item {Developed an IaC pipeline using Atlantis, ensuring version-controlled infrastructure changes and promoting consistency and reproducibility.}
        \item {Collaborated with cross-functional teams to configure and manage Azure storage accounts, databases, Redis cache, and Azure Active Directory (AD), ensuring optimal performance and security.}
      \end{cvitems}
    }

    
%---------------------------------------------------------
  \cventry
    {Consultant DevOps Engineer (Freelance)} % Job title
    {Redify s.r.l} % Organization
    {remote,  Bologna - Italy} % Location
    {Feb. 2024 - Sep. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Migrated Parker HCL Commerce from VM-based deployment (v8) to Kubernetes-based deployment (v9), ensuring a seamless transition for critical applications.}
        \item {Set up and configured Kubernetes clusters in Azure AKS while tailoring Helm charts using Kustomize to meet Parker's specific requirements.}
        \item {Managed application secrets securely using SOPS integrated with ArgoCD, supporting multiple values files for environment-specific configurations.}
        \item {Developed an ArgoCD custom plugin to enable the combined use of Kustomize and Helm, enhancing deployment flexibility and efficiency.}
        \item {Oversaw Azure DevOps pipelines, managing workers and writing pipelines for deploying applications into Kubernetes clusters.}
        \item {Implemented Argo Rollouts for Blue-Green Deployments, dynamically modifying deployments into argo rollouts at runtime through Kustomize to maintain compatibility with community-provided Helm charts.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Architect (Freelance)} % Job title
    {ChaiOne Inc.} % Organization
    {remote, Houston, TX 77002, USA} % Location
    {MaY. 2022 - Apr. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected a hybrid deployment architecture for the Terminal Management System (TMS), enabling seamless integration of on-premises and cloud-based infrastructure.}
        \item {Developed Terraform code to provision and manage AWS infrastructure, including VPC, EC2, CloudFront, S3, EKS, ECR, and other related services, ensuring scalability, security, and high availability.}
        \item {Created Helm charts to streamline the deployment of the TMS application on EKS.}
        \item {Implemented Azure DevOps for continuous integration and continuous deployment (CI/CD) of applications, automating the build, test, and deployment processes.}
        \item {Successfully deployed the TMS application on edge devices connected through site-to-site VPN, ensuring reliable and secure access to critical systems.}
        \item {Utilized CoreOS to create ISO images for deploying the edge devices, simplifying the deployment process and ensuring consistency across multiple devices.}
        \item {Leveraged k3s to deploy the TMS application on edge devices using Helm charts, optimizing resource utilization and improving performance.}
        \item {Created AWS infrastructure for the IoT application, ensuring scalability, security, and high availability, and implemented CI/CD pipelines to automate deployment across multiple environments using Terraform.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Site Reliability Engineer} % Job title
    {edX LLC.} % Organization
    {remote, MA US} % Location
    {May. 2021 - May. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed huge AWS infrastructure for 50+ microservices used by millions of users world wide.}
        \item {Managed IaC using Terraform and imported Existing AWS Infrastructure to Terraform with respect to environments.}
        \item {Migrated legacy service from auto scaling group to Elastic Kubernetes Service.}
        \item {Worked on ArgoCD to deploy microservices on kubernetes.}
        \item {Wrote helm charts for microservices.}
        \item {Wrote bunch of python scripts to automate regular maintenance jobs.}
        \item {Served OnCall Rotation on weekly basis.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior DevOps Engineer} % Job title
    {Emumba. Pvt., Ltd.} % Organization
    {Islamabad, Pakistan} % Location
    {Dec. 2019 - May. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked as a DevOps architect in the team to deploy web application in Google Cloud Platform that was being used in Cisco Live 2020 and 2021}
        \item {It scaled to 150 application nodes and 32 database nodes during the event to handle a peak of 85,000 and an average load of 40,000 requests per second for a three days global event.}
        \item {Monitoring of Infrastructure and Application using Datadog.}
        \item {Lead a team of 3 people and also directly communicated with client to gather the requirements, present the accomplished work and get their feedback.}
        \item {Managing data pipeline for millions of telecom devices using Kafka}
        \item {Benchmarking data Ingestion from Kafka into Amazon Redshift and Druid databases.}
        \item {Benchmarking Amazon Redshift, Timescale DB and Apache Druid for query performance.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps and Data Engineer} % Job title
    {AN10 Pvt., Ltd.} % Organization
    {Islamabad, Pakistan} % Location
    {Apr. 2018 - Nov. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked in small team at early stage of startup and learned to work in true DevOps culture.}
        \item {Worked for the design, development and deployment of scalable micro services based IoT platform.}
        \item {Worked on ETL pipelines using python processors and kafka for streaming and batch processing.}
        \item {Created Gitlab-CI pipelines for building, testing and deploying the platform.}
        \item {Managed AWS and GCP infrastructure for platform deployment.}
        \item {Deployed and Managed Kafka, Elasticsearch and Cassandra clusters}
        \item {Wrote OLAP queries in Spark SQL and optimizing them for Big Data.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Design Engineer} % Job title
    {xFlow Research Inc.} % Organization
    {Islamabad, Pakistan} % Location
    {Jan. 2017 - Mar. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and optimized software solutions for network traffic analysis and performance monitoring systems.}
        \item {Collaborated with cross-functional teams to design scalable software architectures for high-throughput data processing.}
        \item {Implemented automated testing frameworks and contributed to continuous integration processes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Design Engineer} % Job title
    {Plumgrid Inc.} % Organization
    {Islamabad, Pakistan} % Location
    {Dec. 2015 - Jan. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and developed network virtualization solutions and Software-Defined Networking (SDN) components.}
        \item {Worked on OpenStack integration and network overlay technologies for cloud infrastructure.}
        \item {Contributed to the development of distributed systems and network control plane software.}
        \item {Participated in code reviews, technical documentation, and agile development processes.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
